\tool: Programmable, Efficient, and Scalable \\ Secure Two-Party Computation for Machine Learning

### 2018-05-07 ccs/eval.tex
tweaks

\subsection{Secure code partitioning}
\label{sec:pipeeval}
The largest benchmark of \minion~\cite{minionn} is a DNN for CIFAR-10
dataset~\cite{cifar}. 
The classifier's task is to categorize colored ($32\times 32$) images
into 10 classes. A secure evaluation of this DNN needs more memory
than what is available
on our machines. Therefore, we use partitioning and divide the
computation into seven stages. 
The first step does a convolution with 64 output channels and a ReLU
activation. The next four stages together perform a convolution that
involves multiplying a $64\times 576$ matrix with a 
$576\times 1024$ matrix. The sixth stage performs a ReLU and a
convolution. The final stage has four convolutions, five ReLUs, and a
fully connected layer. The total number of lines of \tool code for
this benchmark is 336 lines.

@@

\subsection{Subsequent Work}
Subsequent to our work, there have been improvements in the cryptographic backends.
For example, Gazelle describes specialized protocols for DNNs---which use a 
lattice-based packed additively homomorphic encryption scheme (PAHE) for arithmetic computations and garbled circuits for boolean computations---that can evaluate the CNN benchmark of Table~\ref{tab:nn} in 0.8 seconds (as opposed to
5.1 seconds taken by \tool when using ABY). Such advances in cryptography are
orthogonal to our contributions. In particular, we are interested in using Gazelle
as our backend when it becomes available. Furthermore, the authors of Gazelle remark:
``A final, very interesting and ambitious line
of work would be to build a compiler that allows us to easily
express arbitrary computations and automatically factor the
computation into PAHE and two-party primitives.''
\tool addresses this exact problem of factoring computations into
arithmetic and boolean parts.

>>>>

\subsection{Secure code partitioning}
\label{sec:pipeeval}
\aseem{Is it worth splitting it into microbenchamrking first, which is
  Fig. 11, and then comparison with others? Right now, Fig. 11 text
  just comes at the end, should be highlight it in a paragraph or
  something?}
The largest benchmark of \minion~\cite{minionn} is a DNN for CIFAR-10
dataset~\cite{cifar}. 
The classifier's task is to categorize colored ($32\times 32$) images
into 10 classes. A secure evaluation of this DNN needs more memory
than what is available
on our machines. Therefore, we use partitioning and divide the
computation into seven stages. 
The first step does a convolution with 64 output channels and a ReLU
activation. The next four stages together perform a convolution that
involves multiplying a $64\times 576$ matrix with a 
$576\times 1024$ matrix. The sixth stage performs a ReLU and a
convolution. The final stage has four convolutions, five ReLUs, and a
fully connected layer. The total number of lines of \tool code for
this benchmark is 336 lines.

@@

\subsection{Subsequent Work}
Subsequent to our work, \aseem{TODO} et al. \aseem{cite} have
presented Gazelle, a framework for specialized DNN
protocols. Gazelle use a lattice-based packed additively homomorphic
encryption scheme (PAHE) for arithmetic computations and garbled
circuits for boolean computations. Gazelle can evaluate the CNN benchmark of
Table~\ref{tab:nn} in 0.8 seconds, as opposed to
5.1 seconds taken by \tool with the ABY backend. Such advances in
cryptographic backends are orthogonal to our contributions. In
particular, once Gazelle is available, we could add it as another
cryptographic backend to \tool. Furthermore, the authors of Gazelle remark:
``A final, very interesting and ambitious line
of work would be to build a compiler that allows us to easily
express arbitrary computations and automatically factor the
computation into PAHE and two-party primitives'' -- the exact problem
that \tool solves.

### 2018-05-07 ccs/ex.tex
tweaks

Using both arithmetic and boolean representations requires conversions between them.
The \tool compiler also
instruments these conversion gates accordingly. For example, in
lines~\ref{line:convacc} and~\ref{line:convb}, the compiler converts
\ls{a\_acc} and \ls{a\_b} to boolean representation, before they are
input to the comparison and multiplexer circuits.
%\vspace{-0.2in}

@@

\subsection{Comparison with Yao-only approach}
Before we provide the formalization of our compiler, we show that for performance it it critical to use a mix of arithmetic and boolean circuits.
We demonstrate the performance benefits of mixed computation over boolean-only compute by comparing with previous tools CBMC-GC~\cite{cbmcgc} and ObliVM~\cite{oblivm} that are based on Yao's garbled circuits. As we already mentioned,  we are not the first to observe that Yao-only approach does not scale well beyond examples with small numbers of multiplications \cite{aby,tasty,autoS,secureml,minionn,chameleon}, especially for large-scale multiplications commonly found in Machine Learning (ML) algorithms -- the main use case of \tool.  
Roughly, multiplying two $64$-bit integers using arithmetic sharing requires only $2$ multiplications, whereas Yao requires at least $4096$ AES operations in the online phase.
Indeed, this is one of the main drivers behind development of various specialized MPC protocols in previous works \cite{secureml,minionn,shafindss} that we compare against in \sectionref{eval}.

@@

\subsection{Cryptographic cost-aware compiler}
\label{sec:ccc}
One of the main challenges for our compiler is to split the compute between arithmetic and boolean parts well. 
As mentioned above, \tool is a cryptographic cost-aware compiler and uses the arithmetic and boolean costs of primitive operators and the inter-conversion costs to make the split. Cryptographic cost of converting an arithmetic share to a boolean share requires computing a garbled circuit for addition that is linear in size. Similarly, the cost of converting from boolean to arithmetic is computing a subtraction circuit inside garbled circuit that is again linear in size. ABY analyses all of these costs by running microbenchmarks for basic operations and interconversions (see Figures 2 and 3 in \cite{aby}). Based on these costs, our compiler has some hard constraints. For example, multiplication should always be performed in arithmetic circuit as the cost of boolean multiplication is much higher than  the cost of coercing from boolean to arithmetic, performing an arithmetic multiplication, and then coercing from arithmetic to boolean ($\sim9x$ more time $\&$ $\sim20x$ more communication in a LAN setting). Since the performance gap between arithmetic and boolean multiplication is quite large, we believe that this choice is optimal for realistic network settings.
However, this is not the case for addition. In \tool, if both the operands of addition are boolean shared, we do the addition using boolean circuit, else we use arithmetic circuit. Hence, addition may be done in arithmetic or boolean depending on the operands. 
Finally, all the boolean operations such as comparison, shifts, multiplexors, etc are done using Yao.
We note that doing an optimal split between arithmetic and boolean is an NP-hard problem and in this work, we use heuristics based on costs observed using microbenchmarking. 
For the smaller benchmarks of our evaluation, we wrote ABY code directly and the circuits
generated by our compiler had about the same size as the  hand written code. 
%Moreover, for our machine learning benchmarks (such as linear classifier, DNNs, etc) these choices seem optimal.

>>>>

Using both arithmetic and boolean representations requires conversions between them.
The \tool compiler also
instruments these conversion gates accordingly. For example, in
lines~\ref{line:convacc} and~\ref{line:convb}, the compiler converts
\ls{a\_acc} and \ls{a\_b} to boolean representation, before they are
input to the comparison and multiplexer circuits. \aseem{Question: why
  is b arithmetic to begin with? Can this input be boolean and then we
  don't have to insert a conversion gate for it?}
%\vspace{-0.2in}

@@

\subsection{Comparison with Yao-only approach}
\aseem{We decided to put it here, but reading now, this subsection
  seems to be a bit misplaced to me. How about moving it to 6.1, the
  first subsection in the
  Evaluation? And we can add a couple of lines about it in the
  introduction evaluation paragraph (We first show that mixed
  protocols are much more efficient than Yao only by comparing with
  blah blah). Here it seems quite abrupt, we
  are talking about EzPC at a high-level, with compiler features
  etc. and suddenly details about numbers, CIFAR and what not start
  coming. Seems too soon.}
Before we provide the formalization of our compiler, we show that for performance it it critical to use a mix of arithmetic and boolean circuits.
We demonstrate the performance benefits of mixed computation over boolean-only compute by comparing with previous tools CBMC-GC~\cite{cbmcgc} and ObliVM~\cite{oblivm} that are based on Yao's garbled circuits. As we already mentioned,  we are not the first to observe that Yao-only approach does not scale well beyond examples with small numbers of multiplications \cite{aby,tasty,autoS,secureml,minionn,chameleon}, especially for large-scale multiplications commonly found in Machine Learning (ML) algorithms -- the main use case of \tool.  
Roughly, multiplying two $64$-bit integers using arithmetic sharing requires only $2$ multiplications, whereas Yao requires at least $4096$ AES operations in the online phase.
Indeed, this is one of the main drivers behind development of various specialized MPC protocols in previous works \cite{secureml,minionn,shafindss} that we compare against in \sectionref{eval}.

@@

%% \subsection{Cryptographic cost-aware compiler}
%% \label{sec:ccc}
%% One of the main challenges for our compiler is to split the compute between arithmetic and boolean parts well. 
%% As mentioned above, \tool is a cryptographic cost-aware compiler and uses the arithmetic and boolean costs of primitive operators and the inter-conversion costs to make the split. Cryptographic cost of converting an arithmetic share to a boolean share requires computing a garbled circuit for addition that is linear in size. Similarly, the cost of converting from boolean to arithmetic is computing a subtraction circuit inside garbled circuit that is again linear in size. ABY analyses all of these costs by running microbenchmarks for basic operations and interconversions (see Figures 2 and 3 in \cite{aby}). Based on these costs, our compiler has some hard constraints. For example, multiplication should always be performed in arithmetic circuit as the cost of boolean multiplication is much higher than  the cost of coercing from boolean to arithmetic, performing an arithmetic multiplication, and then coercing from arithmetic to boolean ($\sim9x$ more time $\&$ $\sim20x$ more communication in a LAN setting). Since the performance gap between arithmetic and boolean multiplication is quite large, we believe that this choice is optimal for realistic network settings.
%% However, this is not the case for addition. In \tool, if both the operands of addition are boolean shared, we do the addition using boolean circuit, else we use arithmetic circuit. Hence, addition may be done in arithmetic or boolean depending on the operands. 
%% Finally, all the boolean operations such as comparison, shifts, multiplexors, etc are done using Yao.
%% We note that doing an optimal split between arithmetic and boolean is an NP-hard problem and in this work, we use heuristics based on costs observed using microbenchmarking. 
%% For the smaller benchmarks of our evaluation, we wrote ABY code directly and the circuits
%% generated by our compiler had about the same size as the  hand written code. 
%Moreover, for our machine learning benchmarks (such as linear classifier, DNNs, etc) these choices seem optimal.

\section{Cryptographic cost-awareness}

In this section we explain various heuristics that \tool uses to split
the secret computation in a program between arithmetic and
boolean. While an optimal split in general is an NP-hard problem
\aseem{can we cite something?}, \tool heuristics are empirically based
on micro-benchmarking, and perform well on the various secure
prediction benchmarks (Section~\ref{sec:eval}).

\paragraph{Micro-benchmarking.} The cost of splitting the compuation
between arithmetic and boolean involves the cost of operations
(addition, multiplication, etc.) and the cost of inter-conversion
gates between arithmetic and boolean. Cryptographic cost of converting
an arithmetic share to a boolean share requires computing a garbled
circuit for addition that is linear in size. Similarly, the cost of
converting from boolean to arithmetic is computing a subtraction
circuit inside garbled circuit that is again linear in size. Demmler
et al.~\cite{aby} analyze all these costs by running
microbenchmarks for basic operations and interconversions (Figures
2 and 3 in \cite{aby}). \tool heuristics are based on these results.

\paragraph{Multiplication.} For multiplication, \tool always chooses
arithmetic circuit, as the cost of boolean multiplication is much
higher than the cost of coercing the operands from boolean to
arithmetic, performing an arithmetic multiplication, and then coercing
the result back to boolean ($\sim9x$ more time $\&$ $\sim20x$ more
communication in a LAN setting). Since the performance gap is quite
large, we believe that this choice is optimal for realistic network
settings.

\paragraph{Addition.} However, this is not the case for addition. If
both the operands of addition are boolean shared, \tool performs
addition using a boolean circuit, else it uses an arithmetic
circuit. \aseem{What if one operand is in boolean and the other is in
  arithmetic?} Hence, addition may be done in arithmetic or boolean
depending on the operands.

\paragraph{Boolean operations.} Finally, \tool chooses Yao for for all
the boolean operations such as comparison, shifts, multiplexors,
etc. \aseem{Can we write a sentence here that Demmler et al. show this
  is the optimal choice?}

### 2018-05-07 ccs/intro.tex
tweaks

 Today it is hard for developers to program secure applications
 using cryptographic techniques. Typical developers lack a deep
 understanding of cryptographic protocols, and cannot be
 expected to use them correctly and efficiently on their own.
 Ideally, a developer would declare the functionality in a general
 purpose, high-level programming language and a
 tool, e.g., a compiler would generate an efficient protocol that
 implements the functionality securely, while hiding the cryptography
 behind-the-scenes.

@@

%Since its introduction in 1980s, there has been a long
%sequence of work that has transformed 2PC from a mere theoretical tool to
%something practically efficient and usable.
%Our goal is to build a framework that enables programmers, who are not
%experts in cryptography, to easily program efficient and scalable \mpc
%protocols. 
To understand the
state-of-the-art, let us consider an example underlying many
secure prediction algorithms. Suppose Alice wants to write
a \mpc protocol to securely
compute $w^Tx >b$. Here $w$ (a vector) and $b$ (a scalar) constitute
the server classifier, and $x$ is the client's input vector. Further,
$\cdot^{T}$ is the matrix transpose operator, and $w^Tx$ denotes the
inner product of  $w$ and $x$. Alice has the following options.

@@

This paper presents \tool\footnote{Read as ``easy peasy'',
stands for Easy 2 Party Computation.}, the first
``cryptographic-cost aware'' framework that generates efficient and
scalable \mpc protocols from high-level programs devoid of any
cryptographic details. 
The generated protocols use combinations of
arithmetic and boolean circuits that introduce unique compilation challenges.
Standard compilers do not attempt to reason about or insert non-trivial type casts
and require the programmers to perform them explicitly. 
We back \tool with formal semantics that enable the compiler to
insert type conversions between boolean and arithmetic components
while maintaining provable correctness, security, and efficiency.
The automatically generated protocols have performance comparable to
or better than the custom, specialized
protocols from previous works~\cite{shafindss,wu,minionn,secureml,cryptonets,valeriaMatrix}.
In fact, these papers (and others) cite the inefficiency of generic \mpc as the major motivation
behind the design of specialized protocols. Using \tool, we empirically  demonstrate
that generic \mpc implementations are much more efficient than what they were believed to be. 
 %(up to a factor of 19x in our
%experiments, depending on the functionality) \nc{I added this but I
%  guess we are saying it many times, but might be nice to highlight
%  perf early no?} \aseem{My rationale was to save the numbers for
%  Evaluation summary and remain high-level here.} 
Below we describe
the salient features of \tool.

@@

\paragraph{Scalability (secure code partitioning).} \mpc tools
often do not scale to large functionalities. The reason is that
most \mpc implementations use a circuit-like representation as an
intermediate language. Hence, the largest compute that can be done
securely is upper-bounded by the largest circuit that can fit in the
machine memory\footnote{Using swap and
disk space is feasible but it causes huge slowdown.}. This is a
show-stopper for applications like secure machine learning, secure
prediction, etc. that operate on large amounts of data.
%\aseem{Can we
%cite something here to support this claim?}
\tool addresses the scalability concern using a novel technique that
we call secure code partitioning (or partitioning in short). At
a high level, we decompose the original program into a sequence of small
sub-programs, which are then sequentially processed by \tool, while
appropriately threading the intermediate outputs
along. While this
addresses the scalability concern (i.e., the circuit
sizes of the sub-programs are now small enough to fit in the memory),
we still have to address
the security risk of revealing the intermediate outputs. \tool comes
to the rescue; it automatically inserts the required instrumentation
to ensure security of these intermediate outputs (\sectionref{pipe}). As
we show in our
evaluation, partitioning allows us to program large applications
in \tool.

@@

\paragraph{Formal guarantees.} We prove formal correctness and
security theorems for our compiler. The correctness theorem relates the
``trusted third party'' semantics of a source
program and the ``protocol'' semantics (the distributed \mpc
semantics that relies on circuit evaluation) of the corresponding
compiled program. The theorem
guarantees that for all well-typed source programs, the two semantics
successfully terminate
(e.g., there are no array index out-of-bounds errors) with identical
observable outputs. For
the security theorem, we formally reduce the security
of our scheme against semi-honest (or, ``honest but curious")
adversaries to the semi honest security of the  \mpc back-end. The
theorem provides protection against side-channels arising from
conditionals and memory access patterns.
 We also prove a formal security theorem against semi-honest
 adversaries for our partitioning
scheme (\sectionref{ld} and~\sectionref{pipe}).

>>>>

 Today it is hard for developers to program secure applications
 using cryptographic techniques. Typical developers lack a deep
 understanding of cryptographic protocols, and cannot be
 expected to use them correctly and efficiently on their own.
 Ideally, a developer would declare the functionality in a general
 purpose, high-level programming language and a
 tool, e.g. a compiler, would generate an efficient protocol that
 implements the functionality securely, while hiding the cryptography
 behind-the-scenes.

@@

%Since its introduction in 1980s, there has been a long
%sequence of work that has transformed 2PC from a mere theoretical tool to
%something practically efficient and usable.
%Our goal is to build a framework that enables programmers, who are not
%experts in cryptography, to easily program efficient and scalable \mpc
%protocols. 
To understand the
state-of-the-art, let us consider an example underlying many
secure prediction algorithms. Suppose Alice wants to write
a \mpc protocol to securely
compute $w^Tx >b$. Here $w$ (a vector) and $b$ (a scalar) constitute
the server classifier, and $x$ is the client's input vector. Further,
$\cdot^{T}$ is the matrix transpose operator, and $w^Tx$ denotes the
inner product of  $w^T$ and $x$. Alice has the following options.

@@

This paper presents \tool\footnote{Read as ``easy peasy'',
stands for Easy 2 Party Computation.}, the first
``cryptographic-cost aware'' framework that generates efficient and
scalable \mpc protocols from high-level programs devoid of any
cryptographic details. 
The generated protocols use combinations of
arithmetic and boolean circuits that introduce unique compilation challenges.
Standard compilers do not attempt to reason about or insert non-trivial type casts
and require the programmers to perform them explicitly. \aseem{This
last sentence and the bit about unique compilation challenges seems
unnecessary to me. Compilers do insert type casts automatically. Also
at this point in the paper the words ``type casts'' don't mean much.}
We back \tool with formal semantics that enable the compiler to
insert type conversions between boolean and arithmetic components
while maintaining provable correctness, security, and
efficiency. \aseem{Provable efficiency? Perhaps provable should
be rescoped. And again, type conversions may not be clear at this
point. I would simply say that EzPC inserts inter-conversion gates
automatically. It is backed by a formal model and provides
provable correctness and security, and efficiency.}
The automatically generated protocols have performance comparable to
or better than the custom, specialized
protocols from previous works~\cite{shafindss,wu,minionn,secureml,cryptonets,valeriaMatrix}.
In fact, these papers (and others) cite the inefficiency of generic \mpc as the major motivation
behind the design of specialized protocols. Using \tool, we empirically  demonstrate
that generic \mpc implementations are much more efficient than what they were believed to be. 
 %(up to a factor of 19x in our
%experiments, depending on the functionality) \nc{I added this but I
%  guess we are saying it many times, but might be nice to highlight
%  perf early no?} \aseem{My rationale was to save the numbers for
%  Evaluation summary and remain high-level here.} 
Below we describe
the salient features of \tool.

@@

\paragraph{Scalability (secure code partitioning).} \mpc tools
often do not scale to large functionalities. The reason is that
most \mpc implementations use a circuit-like representation as an
intermediate language. Hence, the largest compute that can be done
securely is upper-bounded by the largest circuit that can fit in the
machine memory\footnote{Using swap and
disk space is feasible but it causes huge slowdown.}. This is a
show-stopper for applications like secure machine learning, secure
prediction, etc. that operate on large amounts of data.
%\aseem{Can we
%cite something here to support this claim?}
\tool addresses the scalability concern using a novel technique that
we call secure code partitioning (or partitioning in short). At
a high level, we decompose the original program into a sequence of small
sub-programs, which are then sequentially processed by \tool, while
appropriately threading the intermediate outputs
along. While this
addresses the scalability concern (i.e., the circuit
sizes of the sub-programs are now small enough to fit in the memory),
we still have to address
the security risk of revealing the intermediate outputs. \tool comes
to the rescue; it automatically inserts the required instrumentation
to ensure security of these intermediate outputs (\sectionref{pipe}). As
we show in our
evaluation, partitioning allows us to program large applications
in \tool. \aseem{What about the differences from Yao pipelining? Worth
adding here that it is a backend-agnostic technique?}

@@

\paragraph{Formal guarantees.} We prove formal correctness and
security theorems for our compiler. The correctness theorem relates the
``trusted third party'' semantics of a source
program and the ``protocol'' semantics (the distributed \mpc
semantics that relies on circuit evaluation) of the corresponding
compiled program. The theorem
guarantees that for all well-typed source programs, the two semantics
successfully terminate
(e.g., there are no array index out-of-bounds errors) with identical
observable outputs. For
the security theorem, we formally reduce the security
of our scheme against semi-honest (or ``honest but curious")
adversaries to the semi honest security of the  \mpc back-end. The
theorem provides protection against side-channels arising from
conditionals and memory access patterns.
 We also prove a formal security theorem against semi-honest
 adversaries for our partitioning
scheme (\sectionref{ld} and~\sectionref{pipe}).
